---
title: "p8105_hw1_tw2838"
author: "Tianyou Wang"
date: "2022-09-24"
output: html_document
---

# Problem #1 Penguins Dataset

## Load and describe the dataset

Now, we are loading the `penguins` dataset
```{r}
data("penguins", package = "palmerpenguins")
```
In the `penguins` dataset, we have characteristic variables, including species, island, and sex. The numeric variables include bill lenghs in millmeters, bill depth in millmeters, flipper length in millmeters, body mass in grams, and year.

This data set include `r nrow(penguins)` rows and `r ncol(penguins)` columns.

To get the mean flipper length, I excluded the missing values and rounded up to 2 decimal place. 
The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

## Scatterplot of flipper_length vs bill_length

```{r}
library(tidyverse)

df = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  z = penguins$species
  )

ggplot(df, aes(x = penguins$bill_length_mm , y = penguins$flipper_length_mm, color=z) )+ geom_point()
```

Save the scatter plot into the local R project file.
```{r}
ggsave("scatter_plot_penguins.pdf", height = 4, width = 6)
```







