---
title: "p8105_hw1_tw2838"
author: "Tianyou Wang"
date: "2022-09-24"
output: github_document
---

# **Problem #1**

## Load and Describe the Penguins Dataset

Now, we are loading the `penguins` dataset
```{r}
data("penguins", package = "palmerpenguins")
```
In the `penguins` dataset, we have characteristic variables, including species, island, and sex. The numeric variables include bill lenghs in millmeters, bill depth in millmeters, flipper length in millmeters, body mass in grams, and year.

This data set include `r nrow(penguins)` rows and `r ncol(penguins)` columns.

To get the mean flipper length, I excluded the missing values and rounded up to 2 decimal place. 
The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.



## Scatterplot of Flipper_length vs Bill_length

```{r warning = FALSE}
library(tidyverse)

dfQ1 = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  z = penguins$species
  )

ggplot(dfQ1, aes(x = penguins$bill_length_mm , y = penguins$flipper_length_mm, color = z) ) +  geom_point()
```

Save the scatter plot into the local R project file.
```{r warning = FALSE}
ggsave("scatter_plot_penguins.pdf", height = 4, width = 6)
```



# **Problem #2**

## Create the Data Frame

```{r}
dfQ2 = tibble(
  var_random = rnorm(10),
  var_logic = var_random > 0,
  var_char = c ("A","A","A","B","B","B","C","C","C","C" ),
  var_fac = factor(c("high","high","high","medium","medium","medium","low","low","low","low"))
)
print(dfQ2)
```



## Mean for Each Variables
```{r}
mean(dfQ2$var_random)
```
We get the mean for the random variable since it is a numeric variable. The mean is `r mean(dfQ2$var_random)`. 


```{r}
mean(dfQ2$var_logic)
```
We get the mean for the logic variable since the true is treated at "1" and the false is treated as "0." The mean is `r mean(dfQ2$var_logic)`.


```{r warning = FALSE}
mean(dfQ2$var_char)
mean(dfQ2$var_fac)
```
We don't have means for the character and factor variables since they are not numerical or factorial. 



## Convert to Numeric Variables
```{r eval = FALSE}
as.numeric(dfQ2$var_logic)
```
R assigned "1" for "TRUE" and "0" for FAlSE."


```{r warning = FALSE, eval = FALSE}
as.numeric(dfQ2$var_char)
```
R failed to assign numeric values for the character variable. The Warning showed that NAs were introduced by coercion. 


```{r eval = FALSE}
as.numeric(dfQ2$var_fac)
```
R successfully assigned numeric value for each levels. 
